A demonstration of the \LaTeXe\ class file for \itshape{\journalnamelc}\footnotemark[2]

### 2019-02-03 journal/conclusions.tex
add one more tstl ref

More practically, we would like to tightly integrate our approach with
automated test generation tools, such as TSTL \cite{tstlsttt,NFM15},
DeepState \cite{DeepState,DeepStateTutorial}, Echidna \cite{Echidna}, and
Manticore \cite{Manticore}.  Automated test generation tools tend to produce a
large number of passing and failing tests, and are often used in
``overnight'' runs where adding a step to use mutants to triage
failing tests and provide localization suggestions for the highly
ranked tests may not even impose a noticable overhead on current usage
practices.  The latter two tools (Echidna and Manticore), which target smart
contracts for the Ethereum blockchain \cite{wood2014ethereum}, are
particularly promising opportunities, because the gas-limited computation bounds of the Ethereum
Virtual Machine essentially guarantee that smart contract code is
small enough to make mutation analysis cheap.  The availability of a
multi-language mutation analysis tool \cite{RegExpMut} supporting
Python, C/C++, and Solidity (the language used for most smart
contracts) means that a common infrastructure base can be shared by
all of these tool integrations.

>>>>

More practically, we would like to tightly integrate our approach with
automated test generation tools, such as TSTL \cite{tstlsttt,NFM15,ISSTA15},
DeepState \cite{DeepState,DeepStateTutorial}, Echidna \cite{Echidna}, and
Manticore \cite{Manticore}.  Automated test generation tools tend to produce a
large number of passing and failing tests, and are often used in
``overnight'' runs where adding a step to use mutants to triage
failing tests and provide localization suggestions for the highly
ranked tests may not even impose a noticable overhead on current usage
practices.  The latter two tools (Echidna and Manticore), which target smart
contracts for the Ethereum blockchain \cite{wood2014ethereum}, are
particularly promising opportunities, because the gas-limited computation bounds of the Ethereum
Virtual Machine essentially guarantee that smart contract code is
small enough to make mutation analysis cheap.  The availability of a
multi-language mutation analysis tool \cite{RegExpMut} supporting
Python, C/C++, and Solidity (the language used for most smart
contracts) means that a common infrastructure base can be shared by
all of these tool integrations.
